\clearpage
\chapter{Introduction}
\label{chap:introduction}

As the robotics industry develops, it is becoming increasingly common to see robots used to solve both important, difficult and dangerous tasks. Dealing with real world problems is often the goal when inventors work towards new technologies. Some inventions may be used in a multitude of ways and further the development of other increasingly complex solutions, while others serve society in small but significant ways for decades to come.
As the technologies mature and become more widely available, new possibilities arise. Possibilities to use the technology for less serious tasks and instead focus on showing its capabilities in a fun and eye-catching way. This could be done by using it in an unconventional environment or by completing a task far outside the intend of the inventor.
This project will try to use technology in such a way. It will try to use methods originally developed for the industry to complete an objective it was not intended for.

\section{Project Goals}

Using a UR5 robot arm with an attached gripper, a camera, and software, the aim of this project is to pick up a ball and throw it at a dart board placed within view of the camera. For safety reasons the ball thrown is light weight, made of plastic and is about the size of a ping pong ball. To allow it to stick to the dart board, it is coated with Velcro, just as the dart board is. Success will be measured based on how far the average throw is from the bullseye.

\section{Problem Definition}

\textbf{Make a UR5 robot arm throw an object at a designated target}
\begin{itemize}
	\item Identify the target point using machine vision
	\item Plan a trajectory for the object using physics and kinematics
	\item Control a UR5 and gripper based on modeled trajectory
\end{itemize}
The solution is expected to consistently hit within the visual bullseye of the Velcro dart board, as seen in \textcolor{red}{figure \ref{fig:dartboard}}. Specifically, the center of the ball should be within 2 cm of the center of the bullseye. This accuracy would also allow the solution to hit within the opening of a standard American 16 oz red solo cup with a ping pong ball. The accuracy is accepted to be consistent, if at least 90\% of throws hit within the accepted target area.
Additionally, the solution should require no human intervention once started, apart from placing the ball in a designated pickup area at the start of each throw.

\section{Constraints \& Limitations}

\section{System Overview}